Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-23 man/figures/location_map.Rmd
update figures std anomalies and EVI profile
increase size

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE, dpi = 200)
```

@@

![](../../out/fig/geomap/mapa_situacion_v2.jpg){height=600px}

>>>>

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

@@

![](../../out/fig/geomap/mapa_situacion_v2.jpg){height=750px}
